---
title: "p8105_hw6_sc5126"
author: "Si Chen"
date: "`r Sys.Date()`"
output: github_document
---

```{r load_library, warning = FALSE, message = FALSE, include=FALSE}
library(tidyr)
library(tidyverse)
library(rvest)
library(viridis)
library(patchwork)
library(olsrr)
library(mgcv)
library(modelr)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Question 2

# Load data
```{r load_data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```
# Bootstrap $\hat{r}^2$
```{r get_r2}
bootstrap_r2 = 
  weather_df %>%  
  modelr::bootstrap(n=5000) %>%  
  mutate (
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data=df)),
    results = map(models,  broom::glance) 
  ) %>%  
  select(-strap, -models) %>%  
  unnest(results) %>%  
  select(r.squared)

```

```{r plot_r2}
bootstrap_r2 %>% 
  ggplot(aes(x = r.squared)) + geom_density()

```


Here the $\hat{r}^2$ value we derived is high. It has a mean of `r mean(bootstrap_r2$r.squared)`. the bootstrap values of $\hat{r}^2$ ranges from `r min(bootstrap_r2$r.squared)` to `r max(bootstrap_r2$r.squared)`. It can be concluded that `tmin` and `prcp` explained `tmax` decently.


# The 95% intervel for $\hat{r}^2$

```{r calculate_CI_r2}

bootstrap_r2 %>%  
  summarize(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975))

```


## Bootstrap $\log(\beta_1 * \beta2)$
```{r bootstrap_log}

bootstrap_logb1b2 = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data=df)),
    results = map(models, broom::tidy)
    ) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate
    ) %>% 
  rename(
    beta0 = `(Intercept)`, 
    beta1 = tmin,
    beta2 = prcp
    ) %>% 
  mutate(
    log_b1b2 = log(beta1 * beta2)
    )

```



```{r plot_logb1b2}

 bootstrap_logb1b2 %>% 
  ggplot(aes(x = log_b1b2)) + geom_density()

```


Here the distribution of $\log(\beta_1 * \beta2)$ is skewed to the left.

The $\log(\beta_1 * \beta2)$ value we derived has a mean of `r mean(bootstrap_logb1b2$log_b1b2)`. the bootstrap values of $\log(\beta_1 * \beta2)$ ranges from `r min(bootstrap_logb1b2$log_b1b2)` to `r max(bootstrap_logb1b2$log_b1b2)`.


# The 95% intervel for $\log(\beta_1 * \beta2)$

```{r calculate_CI_logb1b2}

bootstrap_logb1b2 %>%  
  summarize(
    ci_lower = quantile(log_b1b2, 0.025, na.rm = TRUE), 
    ci_upper = quantile(log_b1b2, 0.975, na.rm = TRUE))

```



## Question 3



```{r , echo=FALSE}

```


